Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-04-26 manuscript/components/error_table.tex
adds new one step and climate change simulation results

\begin{table}[ht]
\centering
\caption{Accuracy (mean absolute error, MAE) and precision (90\% Distance) 
                  of out of sample predictions. Forecasts were made without random 
                  year effects; only climate covariates could explain year-to-year 
                  variation. 90\% Distance refers to the average distance between the 
                  upper and lower 90th percentiles of the 100 predicted values for 
                  each quadrat-year combination.} 
\begin{tabular}{llrrr}
  \hline
Species & Model & MAE & 90\% Distance & Mean Obs. Cover \\ 
  \hline
BOGR & IPM & 4.03 & 24.74 & 9.43 \\ 
  BOGR & QBM & 2.80 & 29.46 & 8.35 \\ 
  HECO & IPM & 0.34 & 1.87 & 1.15 \\ 
  HECO & QBM & 0.29 & 5.53 & 1.18 \\ 
  PASM & IPM & 0.14 & 0.50 & 0.42 \\ 
  PASM & QBM & 0.17 & 1.57 & 0.42 \\ 
  POSE & IPM & 0.45 & 1.63 & 1.25 \\ 
  POSE & QBM & 0.41 & 3.51 & 1.27 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\centering
\caption{Accuracy (mean absolute error, MAE) and precision (90\% Distance) 
                  of out of sample predictions. Forecasts were made without random 
                  year effects; only climate covariates could explain year-to-year 
                  variation. 90\% Distance refers to the average distance between the 
                  upper and lower 90th percentiles of the 100 predicted values for 
                  each quadrat-year combination.} 
\begin{tabular}{llrrr}
  \hline
Species & Model & MAE & 90\% Distance & Mean Obs. Cover \\ 
  \hline
BOGR & IPM & 4.61 & 22.41 & 8.26 \\ 
  BOGR & QBM & 4.06 & 29.18 & 8.26 \\ 
  HECO & IPM & 0.59 & 1.93 & 1.22 \\ 
  HECO & QBM & 0.60 & 5.64 & 1.22 \\ 
  PASM & IPM & 0.15 & 0.49 & 0.40 \\ 
  PASM & QBM & 0.20 & 1.59 & 0.40 \\ 
  POSE & IPM & 0.71 & 1.66 & 1.23 \\ 
  POSE & QBM & 0.76 & 3.52 & 1.23 \\ 
   \hline
\end{tabular}
\end{table}

### 2016-04-26 manuscript/manuscript.Rmd
adds new one step and climate change simulation results

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{./components/climate_posteriors_figure.png}
  \caption{Posterior distributions of climate effects ($\boldsymbol{\beta}_C$) for each species and vital rate statistical model. Since our priors were constrained via ridge-regression, we highlight climate effects whose 80\% credible intervals do not overlap zero (red for negative coefficients, blue for positive coefficients).}
\end{figure}

>>>>

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/climate_posteriors_figure.png}
  \caption{Posterior distributions of climate effects ($\boldsymbol{\beta}_C$) for each species and vital rate statistical model. Since our priors were constrained via ridge-regression, we highlight climate effects whose 80\% credible intervals do not overlap zero (red for negative coefficients, blue for positive coefficients). Kernel bandwidths of posterior densities were adjusted by a factor of 4 for visual clarity.}
\end{figure}
